---
title: "Assignment03"
author: "Nadine Heubes"
date: "28 11 2020"
output: html_document
---


*1.Read the data provided in the Excel file and “isolate” the tabulated information into a data.frame class.*
```{r}

getwd()
setwd("C:/Users/nheub/Documents/~edu/https-github.com-GeoMOER-Students-Space-mpg-data-analysis-2020-NHeubes/data")

dat <- read.table("C:/Users/nheub/Documents/~edu/https-github.com-GeoMOER-Students-Space-mpg-data-analysis-2020-NHeubes/data/holzeinschlag.csv", header=TRUE, sep=";", dec=",")

saveRDS(dat, file = "C:/Users/nheub/Documents/~edu/https-github.com-GeoMOER-Students-Space-mpg-data-analysis-2020-NHeubes/data/hessen_holzeinschlag.csv")

str(dat)
```
*2.Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees (i.e. a similar kind of information as provided by the summary function).*
```{r}
head(dat)
numc<- c("Eiche","Buche","Buntholz","Fichte","Kiefer", "Insgesamt")
boxplot(dat[, numc], main="Holzeinschlag in Hessen von 1997-2014", xlab="Baumart", ylab="Holzeinschlag",col="brown", border="black")
 
```


*3. Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid (i.e. arrange the figures in a 2 columns and 2 rows layout).*
```{r}
par_org <- par()
par(mfrow = c(2,2))

plot(dat$Eiche~dat$Buche,xlab="Buche", ylab="Eiche", main="Buche/Eiche")
plot(dat$Fichte~dat$Buche, xlab="Buche", ylab="Fichte", main="Buche/Fichte")
plot(dat$Buntholz~dat$Buche, xlab="Buche", ylab="Buntholz", main="Buche/Buntholz")
plot(dat$Kiefer~dat$Buche, xlab="Buche", ylab="Kiefer", main="Buche/Kiefer")


```


*4. Include your opinion on what could be the key message of these figures in two sentence max.*

Bei steigendem Bucheinschlag steigt ebenfalls der Einschlag von Kiefer, Fichte, Eiche und Buntholz.




