---
title: "02 Assignment"
author: "Nadine Heubes"
date: "20 11 2020"
output: html_document
---

# Unmarked Assignment: Loop and Conquer

*1.Implement an if-then-else statement which prints “larger” if the number provided as variable n is larger than 1 and “equal or smaller” otherwise.*


```{r}
n<-2
if (n > 1) {
print("larger")
}else{
print ("equal or smaller")
}
```

*2.Extent a copy of the above statement (i.e. copy the entire if-then-else statement and include it a second time in your script in order to preserve both versions) which returns “equal” and “smaller” explicitly in addition to “larger".*
```{r}
if (n > 1){
print("larger")
} else if(n == 1) {
print("equal")
} else { 
print("smaller")
}
```

*3.Implement a if-then-else statement which prints “even” if the number provided as variable n is even and which prints “odd” otherwise.*
```{r}
if (n %% 2 == 0){
print ("even")
} else {
print("odd")
}
```


*4.Copy the extended larger/equal/smaller if-then-else statement and include it into a for loop which shows that all three options are actually implemented in a correct manner by iterating over n from a number which is smaller 1, exactly 1 and larger than 1.*

```{r}
i<- c(0,1,2)
for (n in i){
if(n>1){
print("larger")
}else if (n ==1){
print ("equal")
}else{
print ("smaller")
}
}
```
*5.Extent a copy of the above loop and modify the loop and if-then-else statement in such a way, that the information on “larger” etc. is not printed on the screen but saved within a vector (i.e. a variable which will hold all three statements in the end). Print the content of this vector after the loop.*
```{r}
for (n in i) {if (n>1)
{
    vector<- append ("larger", vector)
}else if (n==1){
    vector <- append ("equal", vector)
}else if (n<1){
    vector <- append ("smaller", vector)
}
}
print(vector)
```
*6.Extent a copy of the above modified loop in such a way, that the results are not saved in a vector but a list. Print the content of this list after the loop.*
```{r}
a<- list("larger", "equal", "smaller")
for (n in i){
if(n>1){
print(a[1])
}else if (n ==1){
print (a[2])
}else{
print (a[3])
}
}
```
*7.Change the above modified loop in such a way, that the iteration is controlled by a lapply not by a for-loop. Save the returning information from the lapply function in a variable and print the content of this variable after the loop.*





